Apparent preferences for cognitive effort fade when multiple forms of effort and delay are interleaved in a foraging environment

### 2020-07-31 Cost_manuscript.Rmd
added sequential effects of previous offer

``` {r BTW: 16.1.2. AR, echo = FALSE, include = FALSE}
# Idea: do AIC to compare models per participant
# add an AR regressor to track recent quits
logisRHAR <- dataBtw %>%
              filter(Choice < 2) %>%
              group_by(SubjID) %>%
              mutate(AR = seqQuits(Choice)) %>%
              plyr::dlply("SubjID", identity) %>%
              lapply(function(data) {suppressWarnings(glm(Choice ~ Handling + Offer + AR, data = data, family = "binomial"))})

@@

>>>>

``` {r BTW: 16.1.2. AR + sequential effects, echo = FALSE, include = FALSE}
# Idea: do AIC to compare models per participant
# add an AR regressor to track recent quits
logisRHAR <- dataBtw %>%
              filter(Choice < 2) %>%
              group_by(SubjID) %>%
              mutate(AR = seqQuits(Choice)) %>%
              plyr::dlply("SubjID", identity) %>%
              lapply(function(data) {suppressWarnings(glm(Choice ~ Handling + Offer + AR, data = data, family = "binomial"))})

@@

### OFFER HISTORY
# 
# # check if the recent history of offers affects the probability of acceptances
# # the larger the sum of recent rewards, the lower the probability of acceptance (regardless of how far back the sum goes (from 3 to 6))
# # this makes sense, because larger numbers mean that higher offers recently happened, leaving only lower ones available
# # this is mainly for 10 H, but the effect survives when adding H + R
# logisOfferhist <- dataBtw %>%
#   group_by(SubjID) %>%
#   mutate(rollingOffer = ifelse(TrialN < 3, Offer, Reduce(`+`, shift(Offer, 0:2)))) %>%
#   plyr::dlply("SubjID", identity) %>%
#   lapply(function(data) {suppressWarnings(glm(Choice ~ Handling + Offer + rollingOffer, data = data, family = "binomial"))})
# 
# # coefficient summaries
# logistemp <- sapply(logistemp, coefficients)
# 
# # Rank sum test
# rankRHAR <- wilcox.test(logistemp["rollingOffer", ])
# 
# # mixed effects logistic version
# # significant for 10 and 14s Handling
# dat <- dataBtw %>%
#   filter(Handling == 2) %>%
#   group_by(SubjID) %>%
#   mutate(rollingOffer = ifelse(TrialN < 3, Offer, Reduce(`+`, shift(Offer, 0:4)))) 
# summary(glmer(Choice ~ Handling + Offer + rollingOffer + (1 | SubjID), data = dat, family = "binomial"))
```
